### 2022-12-15 paper.tex
methods ok

\end{document}

>>>>

It is known that if $c\equiv c_0$, $G\equiv G_0$ everywhere, then the amplitude $h$ of GW produced by an inspiring binary satisfies
\begin{equation}
    h\propto\frac{\frac{G_0\mathcal{M}}{c_0^3}[\pi \frac{G_0\mathcal{M}}{c_0^3}F(t)]^{2/3}}{r/c_0}\cos[\int 2\pi F(t)\,\d t],
\end{equation}
where $\mathcal{M}$ is the chirp mass of binary and $F$ is the frequency of GW. Therefore in the region $r\leq R$ mentioned above,
\begin{equation}
    h\propto\frac{\frac{G_\text{s}\mathcal{M}}{c_\text{s}^3}[\pi \frac{G_\text{s}\mathcal{M}}{c_\text{s}^3}F(t)]^{2/3}}{r/c_\text{s}}\cos[\int 2\pi F(t)\,\d t],
\end{equation}
and then on Earth,
\begin{equation}
    h\propto\sqrt{\frac{c_\text{s}^4/G_\text{s}}{c_0^4/G_0}}\frac{\frac{G_\text{s}\mathcal{M}}{c_\text{s}^3}[\pi \frac{G_\text{s}\mathcal{M}}{c_\text{s}^3}F(t)]^{2/3}}{d/c_\text{s}}\cos[\int 2\pi F(t)\,\d t],
\end{equation}
where $d$ is the physical distance of binary. Considering the red shift, the amplitude of GW produced by an inspiring binary on Earth satisfies
\begin{equation}
    h\propto\sqrt{\frac{c_\text{s}^4/G_\text{s}}{c_0^4/G_0}}\frac{\frac{G_\text{s}\mathcal{M}}{c_\text{s}^3}[\pi \frac{G_\text{s}\mathcal{M}}{c_\text{s}^3}F(t)]^{2/3}}{d/c_\text{s}}\cos[\int 2\pi \frac{F(t)}{1+z}\,\d t],
\end{equation}
where $z$ is the red shift of binary. If we define $F_\text{obs}(t)=F(t)/(1+z)$ and $\mathcal{M}_\text{obs}=\mathcal{M}(1+z)$, then
\begin{equation}
    h\propto\sqrt{\frac{c_\text{s}^6/G_\text{s}}{c_0^6/G_0}}\frac{\frac{G_\text{s}\mathcal{M}_\text{obs}}{c_\text{s}^3}[\pi \frac{G_\text{s}\mathcal{M}_\text{obs}}{c_\text{s}^3}F_\text{obs}(t)]^{2/3}}{d_\text{L}/c_0}\cos[\int 2\pi F_\text{obs}(t)\,\d t],
\end{equation}
where $d_\text{L}=d(1+z)$ is the luminosity distance of binary. However, in former researches, $h$ was assumed to satisfy
\begin{equation}
    h\propto\frac{\frac{G_0\mathcal{M}_\text{obs}}{c_0^3}[\pi \frac{G_0\mathcal{M}_\text{obs}}{c_0^3}F_\text{obs}(t)]^{2/3}}{d_\text{L}/c_0}\cos[\int 2\pi F_\text{obs}(t)\,\d t],
\end{equation}
therefore, $d_\text{L,G}$, the result of measuring $d_\text{L}$ by using GW observation data and methods in former researches, will satisfy
\begin{equation}
    \sqrt{\frac{G_\text{s}/c_\text{s}^6}{G_0/c_0^6}}=\frac{d_\text{L,G}}{d_\text{L}},
\end{equation}
where $d_\text{L}$ can be also measured precisely by using EMW observation data.

Therefore, we can constrain $c_\text{s}$ and $G_\text{s}$ by comparing $d_\text{L}$ and $d_\text{L,G}$, and $\sqrt{[\frac{1}{2}\Delta\!\ln(G_\text{s}/G_0)]^2+[3\Delta\!\ln(c_\text{s}/c_0)]^2}=\Delta\!\ln(d_\text{L,G}/d_\text{L})$, where $\Delta$ denotes to the uncertainty. The result of measuring $d_\text{L}$ and $d_\text{L,G}$ for GW170817/GRB 170817A is $d_\text{L}=(42.9 \pm 3.2)\text{Mpc}$ and $d_\text{L,G}=40_{-14}^{+8}\text{Mpc}$, and we estimate that this result can constrain $c_\text{s}$ and $G_\text{s}$ as $(G_\text{s}/G_0)^{1/2}(c_\text{s}/c_0)^3=0.9 \pm 0.3$.
\end{document}
